---
title: "Experiment 2 Comparing means"
output: 
      html_notebook:
            toc: yes
            toc_depth: 5
            toc_float: true
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(data.table); library(multcomp); library(compute.es); library(pastecs); library(psych); library(car); library(ez); library(lsr); library(BayesFactor); library(WRS2); library(effsize)
```

```{r, echo=FALSE}
load("../Data/meanErr.RData")
```

```{r, echo=FALSE, message=FALSE}
meanErr <- data.table(trial.meanErr.long)

meanErr$DisplayMode <- droplevels(meanErr$DisplayMode)

offset.err  <- meanErr[TrialNo %in% c(1:5)]
offset.mean <- offset.err[, .(meanErr = mean(meanErr, na.rm = T)), by = c("SubjectNo", "ExpNo", "Familiarity", "DisplayMode")] 
```

# Descriptive stats
```{r}
offset.des.stats <- offset.mean[, .(Mean = mean(meanErr, na.rm = T), STD = sd(meanErr, na.rm = T), N = length(meanErr)), by = c("ExpNo", "Familiarity", "DisplayMode")]
offset.des.stats
```

# Analysis 1: Dark & Strobe: Familiarity + Drift
```{r, echo=FALSE, message=FALSE, warning=FALSE}
offset.mean.1 <- offset.mean[ExpNo != "Lit"]
offset.mean.1$ExpNo <- droplevels(offset.mean.1$ExpNo)
offset.mean.1$DisplayMode <- droplevels(offset.mean.1$DisplayMode)
```

## Check assumptions
### Shapiro test
```{r}
by(offset.mean.1$meanErr, interaction(offset.mean.1$Familiarity, offset.mean.1$DisplayMode), shapiro.test)
```

### Levene's test
```{r}
leveneTest(offset.mean.1$meanErr, interaction(offset.mean.1$Familiarity, offset.mean.1$DisplayMode))
```

## Run ANOVA
### Richness (Dark and Strobe) x Target drift (Continuous and Intermittent) x Familiarity (Familiar and Unfamiliar)
```{r}
m.1 <- aov(meanErr ~ ExpNo * Familiarity * DisplayMode, data = offset.mean.1)
ms.1 <- summary(m.1)[[1]]
ms.1
```

#### Effect size
```{r}
em <- etaSquared(m.1)
em
```

#### Try Bayesian ANOVA
See more information about using `anovaBF` [here](https://richarddmorey.github.io/BayesFactor/#fixed)
```{r}
bfANOVA.1 <- anovaBF(meanErr ~ ExpNo * Familiarity * DisplayMode, data = offset.mean.1)
bfANOVA.1

bf.interaction.rich.familiarity   <- bfANOVA.1[4]/bfANOVA.1[3]; bf.interaction.rich.familiarity
bf.interaction.drift.familiarity  <- bfANOVA.1[13]/bfANOVA.1[7]; bf.interaction.drift.familiarity
bf.interaction.rich.drift         <- bfANOVA.1[10]/bfANOVA.1[6]; bf.interaction.rich.drift
bf.interaction.all                <- bfANOVA.1[18]/bfANOVA.1[17]; bf.interaction.all

```

* Effect of familiarity: BF10 = 4.10
* Effect of richness: BF10 = 247.75
* Effect of drift: BF10 = 1.20
* Interaction between richness and familiarity: BF10 = 1.60
* Interaction between drift and familiarity: BF10 = 0.52
* Interaction between richness and drift: BF10 = 0.21

### Richness (Dark and Strobe) x Familiarity (Familiar and Unfamiliar) in the Intermittent condition
```{r}
m.1.b <- aov(meanErr ~ ExpNo * Familiarity, data = offset.mean.1[DisplayMode == "Intermittent"])
ms.1.b <- summary(m.1.b)[[1]]
ms.1.b
```

#### Effect size
```{r}
em <- etaSquared(m.1.b)
em
```

#### Try Bayesian ANOVA
See more information about using `anovaBF` [here](https://richarddmorey.github.io/BayesFactor/#fixed)
```{r}
bfANOVA.1.b <- anovaBF(meanErr ~ ExpNo * Familiarity, data = offset.mean.1[DisplayMode == "Intermittent"])
bfANOVA.1.b

bf.interaction.rich.familiarity   <- bfANOVA.1.b[4]/bfANOVA.1.b[3]; bf.interaction.rich.familiarity

```

## Some follow-up tests

From the figure, we can see that there is some effect in the *Strobe-Intermittent* condition, whereas in the *Strobe-Continuous* condition, the direction of difference between *Familiar* and *Unfamiliar* is opposite to the prediction.

So first, let's have a look at the interaction between *Continuous* $\times$ *Intermittent* and *Familiar* $\times$ *Unfamiliar*

### ANOVA on the Strobe data
```{r}
strobe.offset.mean <- offset.mean.1[ExpNo == "Strobe"]

m.strobe <- aov(meanErr ~ Familiarity * DisplayMode, data = strobe.offset.mean)
ms.strobe <- summary(m.strobe)[[1]]
ms.strobe
```

#### Effect size
```{r}
em <- etaSquared(m.strobe)
em
```

#### Try Bayesian 
```{r}
bfANOVA.strobe <- anovaBF(meanErr ~ Familiarity * DisplayMode, data = strobe.offset.mean)
bfANOVA.strobe

bfANOVA.strobe[4]/bfANOVA.strobe[3]
```

> So there may be an interaction between *Continuous* $\times$ *Intermittent* and *Familiar* $\times$ *Unfamiliar* in the Strobe condition - it is just short of significance.

Maybe this is sufficient to look at the familiarity effects in *Continuous* and *Intermittent* conditioins respectively.

#### Familiarity effect in the *Strobe-Continuous* condition
```{r}
t.test(meanErr ~ Familiarity, data = strobe.offset.mean[DisplayMode == "Continuous"], var.equal = TRUE, alternative = "less")
ttestBF(strobe.offset.mean[Familiarity == "Familiar" & DisplayMode == "Continuous"]$meanErr, strobe.offset.mean[Familiarity == "Unfamiliar" & DisplayMode == "Continuous"]$meanErr, paired = FALSE, nullInterval = c(-Inf, 0))
```

> No, there is no difference

#### Familiarity effect in the *Strobe-Intermittent* condition
```{r}
t.test(meanErr ~ Familiarity, data = strobe.offset.mean[DisplayMode == "Intermittent"], paired = FALSE, var.equal = TRUE, alternative = "less")

ttestBF(strobe.offset.mean[Familiarity == "Familiar" & DisplayMode == "Intermittent"]$meanErr, strobe.offset.mean[Familiarity == "Unfamiliar" & DisplayMode == "Intermittent"]$meanErr, paired = FALSE, nullInterval = c(-Inf, 0))
```

> So, the *Unfamiliar* group's trajectories are significantly more curved than those of the *Familiar* group.


# Analysis 2: Dark & Strobe & Lit: Familiarity
```{r, echo=FALSE, message=FALSE, warning=FALSE}
offset.mean.2 <- offset.mean[DisplayMode != "Intermittent"]
offset.mean.2$DisplayMode <- droplevels(offset.mean.2$DisplayMode)
```

## Check assumptions
### Shapiro test
```{r}
by(offset.mean.2$meanErr, interaction(offset.mean.2$Familiarity, offset.mean.2$ExpNo), shapiro.test)
```

### Levene's test
```{r}
leveneTest(offset.mean.2$meanErr, interaction(offset.mean.2$Familiarity, offset.mean.2$ExpNo))
```

## Run ANOVA
```{r}
m.2 <- aov(meanErr ~ ExpNo * Familiarity, data = offset.mean.2)
ms.2 <- summary(m.2)[[1]]
ms.2
```

### Effect size
```{r}
em <- etaSquared(m.2)
em
```

### Try Bayesian ANOVA
See more information about using `anovaBF` [here](https://richarddmorey.github.io/BayesFactor/#fixed)
```{r}
bfANOVA.2 <- anovaBF(meanErr ~ Familiarity * ExpNo, data = offset.mean.2)
bfANOVA.2

bfANOVA.2[4]/bfANOVA.2[3]
```

* Effect of *familiarity*: BF10 = 0.28
* Effect of *Richness*: BF10 > 100
* Effect of interaction: BF10 = 0.61


#### Familiarity effect in the *Lit* condition
```{r}
t.test(meanErr ~ Familiarity, data = offset.mean.2[ExpNo == "Lit"], paired = FALSE, var.equal = TRUE, alternative = "less")

ttestBF(offset.mean.2[ExpNo == "Lit" & Familiarity == "Familiar"]$meanErr, offset.mean.2[ExpNo == "Lit" & Familiarity == "Unfamiliar"]$meanErr, paired = FALSE, nullInterval = c(-Inf, 0))
```



