---
title: "Experiment 1 Comparing Means"
output: 
      html_notebook:
            toc: yes
            toc_depth: 5
            toc_float: true
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(data.table); library(multcomp); library(compute.es); library(pastecs); library(psych); library(car); library(ez); library(lsr); library(BayesFactor); library(WRS2); library(effsize)
```

```{r, echo=FALSE}
load("../Data/meanErr.RData")

deflection <- 8.5
```

```{r, echo=FALSE, message=FALSE}
meanErr <- data.table(trial.meanErr.long)

meanErr$DisplayMode <- droplevels(meanErr$DisplayMode)

offset.err  <- meanErr[TrialNo %in% c(1:5) & Collection == "Old"]
offset.mean <- offset.err[, .(meanErr = mean(meanErr, na.rm = T)), by = c("SubjectNo", "Familiarity", "DisplayMode")] 
```

# Descriptive stats
```{r}
offset.des.stats <- offset.mean[, .(Mean = mean(meanErr, na.rm = T), STD = sd(meanErr, na.rm = T), N = length(meanErr)), by = c("Familiarity", "DisplayMode")]
offset.des.stats
```

# Check assumptions
## Shapiro test
```{r}
by(offset.mean$meanErr, interaction(offset.mean$Familiarity, offset.mean$DisplayMode), shapiro.test)
```

## Levene's test
```{r}
leveneTest(offset.mean$meanErr, interaction(offset.mean$Familiarity, offset.mean$DisplayMode))
```

# One-sample test compared to the deflective power of prism on each condition
```{r}
by(offset.mean$meanErr, interaction(offset.mean$Familiarity, offset.mean$DisplayMode), function(x) t.test(x, mu = deflection, alternative = "less"))
```

## Try Bayesian factors for the one-sample tests
```{r}
by(offset.mean$meanErr, interaction(offset.mean$Familiarity, offset.mean$DisplayMode), function(x) ttestBF(x, mu = deflection, nullInterval = c(-Inf, 0)))

```

# Run ANOVA
```{r}
m <- aov(meanErr ~ Familiarity * DisplayMode, data = offset.mean)
ms <- summary(m)[[1]]
ms
```

## Effect size
```{r}
em <- etaSquared(m)
em
```

## Try Bayesian ANOVA
See more information about using `anovaBF` [here](https://richarddmorey.github.io/BayesFactor/#fixed)
```{r}
bfANOVA <- anovaBF(meanErr ~ Familiarity * DisplayMode, data = offset.mean)
bfANOVA

bfANOVA[4]/bfANOVA[3]
```

### Result summary of Bayesian ANOVA
* Effect of *familiarity*: $BF_10$ = 1.45.
* Effect of *target drift*: $BF_10$ = 1.25.
* Effect of interaction: $BF_10$ = 0.39.

# Compare the pairs of conditions
## Continuous vs. Intermittent for the Familiar groups
```{r}
t.test(meanErr ~ DisplayMode, data = offset.mean[Familiarity == "Familiar"], paired = FALSE, var.equal = TRUE, alternative = "less")
ttestBF(offset.mean[Familiarity == "Familiar" & DisplayMode == "Continuous"]$meanErr, offset.mean[Familiarity == "Familiar" & DisplayMode == "Intermittent"]$meanErr, paired = FALSE, nullInterval = c(-Inf, 0))
```

## Continuous vs. Intermittent for the Unfamiliar groups
```{r}
t.test(meanErr ~ DisplayMode, data = offset.mean[Familiarity == "Unfamiliar"], paired = FALSE, var.equal = TRUE, alternative = "less")
ttestBF(offset.mean[Familiarity == "Unfamiliar" & DisplayMode == "Continuous"]$meanErr, offset.mean[Familiarity == "Unfamiliar" & DisplayMode == "Intermittent"]$meanErr, paired = FALSE, nullInterval = c(-Inf, 0))
```

## Familiar vs. Unfamiliar in the Continuous condition
```{r}
t.test(meanErr ~ Familiarity, data = offset.mean[DisplayMode == "Continuous"], paired = FALSE, var.equal = TRUE, alternative = "less" )
ttestBF(offset.mean[Familiarity == "Familiar" & DisplayMode == "Continuous"]$meanErr, offset.mean[Familiarity == "Unfamiliar" & DisplayMode == "Continuous"]$meanErr, paired = FALSE, nullInterval = c(-Inf, 0))
```

## Familiar vs. Unfamiliar in the Intermittent condition
```{r}
t.test(meanErr ~ Familiarity, data = offset.mean[DisplayMode == "Intermittent"], paired = FALSE, var.equal = TRUE, alternative = "less" )
ttestBF(offset.mean[Familiarity == "Familiar" & DisplayMode == "Intermittent"]$meanErr, offset.mean[Familiarity == "Unfamiliar" & DisplayMode == "Intermittent"]$meanErr, paired = FALSE, nullInterval = c(-Inf, 0))
```
